---
title: "COMP2501 Lab Sheet 1"
output:
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

* You are expected to answer the questions in the sheet in class
* You are encouraged to try different code or arguments
* You can discuss with other students for ideas but do not copy from others
* If you have any questions, ask Google, the two TAs, or me
* Sample answers will be given after the class on Moodle

------------------------------------------------------------------------

### Environmental setup

You need to have the `dplyr`, `ggplot2` and `datasets` packages installed. If not yet, please run `install.packages(c("dplyr", "ggplot2", "datasets"))` in your R environment. If you have installed the `tidyverse` package, `dplyr` and `ggplot2` are installed by default.

```{r}
# Load the packages.
library(dplyr)
library(ggplot2)
library(datasets)
```

### 1. Write a function `compute_s_n` that for any given `n` computes the sum `Sn = 1^2 + 2^2 + 3^2 + … + n^2`. Report the value of the sum when `n=100`.

```{r}
compute_s_n <- function(n){
  s = 0
  for (i in 1:n){
    s = s + i^2
  }
  return(s)
}

compute_s_n(100)
```


### 2. Play with the built-in dataset `mtcars` to explore the package `dplyr`. Please use `head()` to show the results if there are too many rows in them.

#### a. Load the dataset `mtcars`. Print 1) the first 6 rows of the data, 2) how many observations (rows) and variables (columns) are in the dataset, 3) the names of all variables.

```{r}


```

#### b. Create a new variable `performance` as the ratio of horsepower (`hp`) to weight (`wt`) (i.e. $perfomance = hp/wt$). Please do operations on a dataset copy of `mtcars` named `mtcars_modified`.

```{r}


```

#### c. 1) Use `top_n()` function to find out the top 1 observation in `mtcars_modified` with the highest value of `performance`, 2) Sort the `mtcars_modified` by `performance` in descending order. Check if the result in 1) is the first row of the results in 2).

```{r}


```

#### d. Filter the original dataset `mtcars` to show only the cars with a mpg value greater than 20. Please do operations on a dataset copy of `mtcars` named `mtcars_filtered`.

```{r}


```

#### e. Select only the `mpg` and `cyl` columns from the filtered dataset `mtcars_filtered`. Please do operations on a dataset copy of `mtcars_filtered` named `mtcars_selected`.

```{r}


```

#### f. Group the dataset `mtcars_selected` by `cyl` and summarize the mean mpg for each group. Please do operations on a dataset copy of `mtcars_selected` named `mtcars_grouped`.

```{r}


```

### 3. Play with the built-in dataset `iris` to explore the package `ggplot2`. Please set an appropriate plot title and axis titles.

#### a. Load the dataset `iris`. Print 1) the first 6 rows of the data, 2) how many observations (rows) and variables (columns) are in the dataset, 3) the names of all variables.

```{r}


```

#### b. Create a scatter plot to visualize the relationship between `Sepal.Length` (x-axis) and `Sepal.Width` (y-axis).

```{r}


```

#### c. Create a scatter plot to visualize the relationship between `Petal.Length` and `Petal.Width`, and color the points by `Species`.

```{r}


```

#### d. Create a boxplot to visualize the distribution of `Petal.Length` of each `Species`.

```{r}


```

#### e. Create a histogram to visualize the distribution of `Petal.Width`.

```{r}


```

#### f. Create a violin plot to visualize the distribution of `Sepal.Length` by `Species`.

```{r}


```

#### g. Create a density plot to visualize the distribution of `Sepal.Width` by `Species`.

```{r}


```

### 4. Practice with the real-world dataset `covid_hk_data` ("http://www.chp.gov.hk/files/misc/enhanced_sur_covid_19_eng.csv"). Please use `head()` to show the results if there are too many rows in them.

#### a. Load the dataset `covid_hk_data`. Print 1) the first 6 rows of the data, 2) how many observations (rows) and variables (columns) are in the dataset, 3) the names of all variables.

```{r}


```

#### b. Filter the dataset `covid_hk_data` with `Case.status.` equal to `Confirmed`. Please do operations on a dataset copy of `covid_hk_data` named `covid_hk_data_filtered`.

```{r}


```

#### c. Group the dataset `covid_hk_data_filtered` by `Report.date`, and calculate the total number of confirmed cases each day (`total_confirmed`). Please do operations on a dataset copy of `covid_hk_data_filtered` named `covid_hk_data_grouped`.

```{r}


```

#### d. Add a new column `date` with the standard date format "YYYY-MM-DD" to the `covid_hk_data_grouped` dataset according to the `Report.date` column. Be reminded the format of `Report.date` is "DD/MM/YYYY". 

```{r}


```

#### e. Use `ggplot2` to visualize the total number of confirmed cases over date with `covid_hk_data_grouped` dataset.

```{r}


```

